---
title: "R Notebook"
output: html_notebook
---

### Load in all the GSEids that we will be analysing


-> Load in your envrioment here (eg. Set GEMMAUSERNAME = "<your password here>")
```{r}
file.edit('~/.Renviron')
```
-> Rember to restart your R session now so the variables are loaded in

- Pipeline the environment variables into the matlab script
- Set timeout prevent crashing -> change if file is larger
```{bash}
echo -e $GEMMAUSERNAME"\n"$GEMMAPASSWORD | timeout 30s /space/opt/matlab/R2018a/bin/matlab -r 'getGemmaInfo("GSEids.csv",0);'
  
```

- Load Original GSE
```{r message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
col_types <- cols('shortName' = col_character())
GSEids_before <- read_csv("GSEids.csv", col_types = col_types)
GSEids_before <- GSEids_before[!duplicated(GSEids_before$shortName), ]
cat("Total ", nrow(GSEids_before), " GSEs for input")
```

- Load data after the getGemmaInfo.m
```{r message=FALSE, warning=FALSE}
library(readr)
GSEid_after <- read_csv("nextGemmaAPI.txt")
GSEid_after <- GSEid_after[!duplicated(GSEid_after$shortName), ]
```

- Find which GSEs are in spreadsheets and in GEMMA
```{r}
count_in <- 0
cat("GSEs that are in GEMMA: ")
for (x in unlist(GSEid_after %>% select("shortName"))) {
  if (count_in %% 10 == 0){
    cat("\n", x, " ")
  }else {
    cat(x, " ")
  }
  count_in <- count_in + 1
}
cat("\n\nTotal GSEs in GEMMA: ",   count_in)
```


- Find what GSEs are in spreadsheet but not in Gemma
```{r}
cat("These are the GSEs not in Gemma: ")
diff <-setdiff(
GSEids_before %>%
  select("shortName") %>% unlist()
,
GSEid_after %>%
  select("shortName") %>% unlist())
count <- 0
for (x in diff) {
  if (count %% 10 == 0){
    cat("\n", x, " ")
    count <- count + 1 
  }else {
    cat("\n", x, " ")
    count <- count + 1 
  }
}
cat("\n\nThere are ", count, " GSEs in total not in Gemma")


```

- Find which GSEs are public and how many
```{r}
count_public <- 0
cat("GSEs that are public in GEMMA: ")
for (x in unlist(GSEid_after %>% filter(isPublic == 1) %>% select("shortName"))) {
  if (count_public %% 10 == 0){
    cat("\n", x, " ")
  }else {
    cat(x, " ")
  }
  count_public <- count_public + 1
}
cat("\n\nThere are ", count_public, " GSEids public")
count_private <- 0
 cat("\n\nThese are the none public GSE in GEMMA: ")
for (x in unlist(GSEid_after %>% filter(isPublic == 0) %>% select("shortName"))) {
  if (count_private %% 10 == 0){
    cat("\n", x, " ")
  }else {
    cat(x, " ")
  }
  count_private <- count_private + 1
}
 cat("\n\nThere are ", count_private, " GSEids public")
```


```{r}
library(gemmaAPI)
no_dea <- c()
setGemmaUser(Sys.getenv("GEMMAUSERNAME"), Sys.getenv("GEMMAPASSWORD"))
for (gse in unlist(GSEid_after %>% select("shortName"))){
  test <- datasetInfo(dataset = gse, request ="differential", memoised=TRUE)
  if (length(test) == 0) {
    no_dea <- c(no_dea, gse)
  }
}
cat("\nThese are the GSEs without DEA: ")
no_dea_count <- 0
for (gse in no_dea) {
   if (count %% 10 == 0){
    cat("\n", gse, " ")
     no_dea_count <- no_dea_count + 1
  }else {
    cat(gse, " ")
    no_dea_count <- no_dea_count + 1
  }
}
cat("\nIn total there are ", no_dea_count, " GSEs without DEA\n")

cat("\nThese are the GSEs with DEA: ")
dea_count <- 0
for (gse in setdiff (GSEid_after %>% select("shortName") %>% unlist(), no_dea))) {
   if (dea_count_DEA %% 10 == 0){
    cat("\n", gse, " ")
     dea_count <- dea_count + 1
  }else {
    cat(gse, " ")
    dea_count <- dea_count + 1
  }
}
cat("\nIn total there are ", dea_count, "GSEs with DEA")
```

```{r}
library(ggplot2)
df <- data.frame(where=c("Not in Gemma", "In Gemma"),
                 count=c(nrow(GSEids_before) - nrow(GSEid_after), nrow(GSEid_after)))
p <- ggplot(data=df, map=aes(x=where, y=count))
p + geom_bar(stat="identity", color="blue", fill="steelblue")  + geom_text(aes(label=count), vjust=1.6, color="black", size=3.5) + theme_classic()
```
```{r}
library(ggplot2)

p <- ggplot(data=GSEid_after, map=aes(x=factor(isPublic, labels=c("Public", "Not Public"))))
p + geom_bar(stat="count", color="blue", fill="steelblue")  + geom_text(aes(label=..count..), stat="count", color="black", size=3.5) + theme_classic()
```
```{r}
library(ggplot2)
df <- data.frame(where=c("Has DEA", "No DEA"),
                 count=c(dea_count, no_dea_count))
p <- ggplot(data=df, map=aes(x=where, y=count))
p + geom_bar(stat="identity", color="blue", fill="steelblue")  + geom_text(aes(label=count), vjust=1.6, color="black", size=3.5) + theme_classic()
```




